Trends of SDR in Thessaloniki

### 2023-09-21 Article.Rmd
Commit 2023-09-21 12:14

In order to compare any features within the trends, we created another set of CUSUMs plots, by subtracting the corresponding long term trend from the data, prior the CUSUM calculation (Figure\ \ref{fig:cusumnotrend}).
With this approach periods where the CUSUM diverge from zero can be interpreted as systematic variation of SDR, further from the climatological mean.

@@

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-1.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-2.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-3.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-4.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-5.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-6.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-7.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-8.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-9.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-10.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-11.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-12.png")
```

>>>>

In order to compare any features within the trends, we created another set of CUSUMs plots, by subtracting the corresponding long term trend from the SDR anomaly data, prior to the CUSUM calculation (Figure\ \ref{fig:cusumnotrend}).
With this approach periods where the CUSUM diverge from zero can be interpreted as systematic variation of SDR, further from the climatological mean.
It is interesting that for the period 1993...... diverge around zero 
and after ~ for all-sky and clear-sky

For cloud-sky .....

@@

```{r echo = FALSE, fig.cap='Distribu.', fig.subcap=c('', '', ''), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics("./images/SzaTrendsSeas-1.png")
knitr::include_graphics("./images/SzaTrendsSeas-2.png")
knitr::include_graphics("./images/SzaTrendsSeas-3.png")
knitr::include_graphics("./images/SzaTrendsSeas-4.png")
knitr::include_graphics("./images/SzaTrendsSeas-5.png")
knitr::include_graphics("./images/SzaTrendsSeas-6.png")
knitr::include_graphics("./images/SzaTrendsSeas-7.png")
knitr::include_graphics("./images/SzaTrendsSeas-8.png")
knitr::include_graphics("./images/SzaTrendsSeas-9.png")
knitr::include_graphics("./images/SzaTrendsSeas-10.png")
knitr::include_graphics("./images/SzaTrendsSeas-11.png")
knitr::include_graphics("./images/SzaTrendsSeas-12.png")
```
